fdcoexist

### 2018-10-09 meta_simulations.Rmd
:sparkles: CWM <-> Env. plots

# Packages ---------------------------------------------------------------------
suppressPackageStartupMessages({
    suppressWarnings({
        library("cowplot")
        library("tidyverse")
        library("directlabels")
    })
})
# Functions --------------------------------------------------------------------
# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = 150) {

@@

    all_env = list(constant          = env_width,
                   constant_strong   = env_width/2,
                   constant_stronger = env_width/3,
                   varying           = var_width)

@@

```{r low_k}
library("furrr")

low_k = 1.15
low_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        low_k)
plan(multiprocess)
tictoc::tic()

low_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul2(x, given_k = low_k)
}, .progress = TRUE)
tictoc::toc()

low_k_simuls_r2 = low_k_simuls %>%
    map(~.x %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)) %>%
    bind_rows()

low_k_simuls_var = low_k_simuls %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var"))

plot_low_k_r2 = ggplot(low_k_simuls_r2, aes(scenario, r.squared)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("R2 of trait2 CWM ~ environment; ", low_k_run_char),
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
plot_low_k_r2

@@

```{r}
high_k = 1.57
high_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        high_k)

@@

```{r varying_A_and_k}
list_A = 2*10^-(seq(4, 6))
list_k = 1 + c(0.05, 0.15, 0.25)

@@

```{r looking_at_slopes}
list_A = 2*10^-(seq(4, 6))
list_k = 1 + c(0.05, 0.15, 0.25)

@@

We want to follow the dynamics through time to understand the variation in Rsquare
```{r}
patch_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        k)

>>>>

# Packages ---------------------------------------------------------------------
suppressPackageStartupMessages({
    suppressWarnings({
        library("cowplot")
        library("tidyverse")
        library("directlabels")
        library("furrr")
    })
})
# Functions --------------------------------------------------------------------
# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = 150) {

@@

    all_env = list(constant          = env_width,
                   constant_strong   = env_width/2,
                   constant_stronger = env_width/5
                # varying           = var_width
                   )

@@

```{r low_k}
# Simulation parameters --------------------------------------------------------
low_k = 1.15
low_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        low_k)

# Actual simulation -----------------------------------------------------------
plan(multiprocess)
tictoc::tic()
low_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, given_k = low_k)
}, .progress = TRUE)
tictoc::toc()

# Compute summaries ------------------------------------------------------------
# Show shape of CWM <-> across situations
low_k_simuls %>%
    bind_rows() %>%
    ggplot(aes(patch_optim, trait2_cwm, color = cor_level,
               group = interaction(cor_level, seed_number))) +
    geom_line(aes(group = interaction(cor_level, seed_number)), alpha = 1/25) +
    geom_smooth(aes(group = cor_level)) +
    facet_grid(rows = vars(compet_status, env_width), cols = vars(scenario)) +
    scale_color_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(x = "Environment",
         y = "Trait 2 CWM",
         subtitle = "CWM <-> Env. Relationship across all simulations")

# Compute slope of CWM <-> Environment relationship
low_k_simuls_slope = low_k_simuls %>%
    map(~.x %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::tidy)) %>%
        unnest(mod_glance) %>%
            filter(term == "patch_optim")) %>%
    bind_rows()

# Gather the variance of traits along environment
low_k_simuls_var = low_k_simuls %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var"))

# Figures ----------------------------------------------------------------------
plot_low_k_slope = ggplot(low_k_simuls_slope, aes(scenario, estimate)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, 1) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("Slope of trait2 CWM ~ environment; ",
                           low_k_run_char),
         x = "Scenario",
         y = "Slope") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
plot_low_k_slope

@@

```{r, eval = FALSE}
high_k = 1.57
high_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        high_k)

@@

```{r varying_A_and_k, eval = FALSE}
list_A = 2*10^-(seq(4, 6))
list_k = 1 + c(0.05, 0.15, 0.25)

@@

```{r looking_at_slopes, eval = FALSE}
list_A = 2*10^-(seq(4, 6))
list_k = 1 + c(0.05, 0.15, 0.25)

@@

We want to follow the dynamics through time to understand the variation in Rsquare
```{r, eval = FALSE}
patch_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        k)
